---
title: 'Data Product: MAP'
author: "Kevin Joy"
date: "12/4/2019"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Maryland Property Data
The [Maryland Open Data Portal](https://opendata.maryland.gov/) provides numerous geographic and non-geographic datasets that are available for search and exploration. Built-in tools allow for visualization of the data in table, graph, dashboard or map format. The Portal is managed by DOIT with contributions from many State and Local agencies.  


This project uses [Real Property Assesment  Data](https://opendata.maryland.gov/Business-and-Economy/Maryland-Real-Property-Assessments-Hidden-Property/ed4q-f8tm/data) to populate home values in Maryland

```{r, echo=F, warning=F, message=F}
library(tidyverse)
library(leaflet)
df = read.csv('rei_data_filt.csv')
#sample
df <- df %>% arrange(desc(price)) %>% head(100)
leaflet() %>%
  addTiles() %>% 
  addMarkers(
    lng = df$lon,
    lat = df$lat,
    popup = paste(sep="<br/>",
                  paste0( "<b>",df$address, "</b>"),
                  paste0("Price: ", format(df$price, big.mark = ",")),
                  paste0("Sqft: ", format(df$living_area, big.mark = ",")),
                  paste0("Year Built: ", df$year_built)
    )
  )

```

```{r,echo=F, warning=F, message=F}
library(DT)
DT::datatable(df)
```
